Title

### 2015-12-10 paper/paper.tex
change dataset numbers
updated subgraph selection section

\usepackage[section]{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{latexsym}
\usepackage{multirow}

@@

\noindent \textbf{Logical form}:
\begin{equation}
\begin{split}
\exists s,d2,p2,c,n: &\\
&\text{instance}(s,want\text{-}01) \wedge \text{instance}(d2, drug) \wedge \\
&\text{instance}(p2, prosecutor) \wedge \text{instance}(c, country) \wedge \\
&\text{instance}(n, name) \wedge \text{arg0}(s,p2) \wedge \text{arg1}(s,d2)
\wedge \\ &\text{arg2}(s,c) \wedge \text{name}(c,n) \wedge \text{op1}(n,
``South") \wedge \\ &\text{op2}(n, ``Korea") \wedge \text{unit}(d2, kilogram)
\wedge \text{quant}(d2, 80)
\end{split}
\end{equation}
\textbf{AMR form}:
\begin{figure}
\includegraphics[width=\linewidth]{amr_example.pdf}
\caption{Example AMR}
\end{figure}

@@

\subsection{Subgraph Selection}

Subgraph selection solves the problem of splitting an AMR graph into a set of
subgraphs which are optimal by some criterion, such that the union of the
subgraphs is the original graph. Said more plainly, the problem is to split a
concept graph into sentences, such that emitting all of the sentences would
communicated all of the concepts in the original graph.

For subgraph selection, we use a logistic regression model. We assumed that the
AMR subgraphs in each of the paragraphs was the correct partitioning of the
merged graph. This means that we had only positive examples in the training
set, so we added negative examples by creating up to $k=100$ other
partitionings of the same merged graph.

Features included the length of the pairwise subgraph similarity, and pairwise
verb overlap between the subgraphs. To determine subgraph similarity, we used
Jaccard similarity, defined to be:
$$J(A,B) = \frac{\lvert A \cap B \rvert}{\lvert A \cup B \rvert}$$

@@

Additionally, we used a simmulated annealing approach, but only for the
subgraph ordering problem.

>>>>

\usepackage[section]{algorithm}
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{latexsym}
\usepackage{multirow}

@@

\noindent \textbf{Logical form}:
\begin{equation}
\begin{split}
\exists s,d2,p2,c,n: &\\
&\text{instance}(s,want\text{-}01) \wedge \text{instance}(d2, drug) \wedge \\
&\text{instance}(p2, prosecutor) \wedge \text{instance}(c, country) \wedge \\
&\text{instance}(n, name) \wedge \text{arg0}(s,p2) \wedge \text{arg1}(s,d2)
\wedge \\ &\text{arg2}(s,c) \wedge \text{name}(c,n) \wedge \text{op1}(n,
``South") \wedge \\ &\text{op2}(n, ``Korea") \wedge \text{unit}(d2, kilogram)
\wedge \text{quant}(d2, 80)
\end{split}
\end{equation}
\textbf{AMR form}:
\begin{figure}
\includegraphics[width=\linewidth]{amr_example.pdf}
\label{fig:amr_example}
\caption{Example AMR}
\end{figure}

@@

\subsection{Subgraph Selection}
\subsubsection{Problem Description}

Subgraph selection solves the problem of splitting an AMR graph into a set of
subgraphs which are optimal by some criterion, such that the union of the
subgraphs is the original graph. Said more plainly, the problem is to split the paragraph-level semantic graph 
into a set sentence-level semantic graphs.

There are $2^{|E|}$ subgraphs for a graph with $|E|$ edges. If we consider every set of $N$ subgraphs, we would have to consider $N^{2^{|E|}}$ sets of subgraphs! Obviously this is infeasible. Fortunately, we can exploit the natural language characteristics of a semantic graph to dramatically reduce the number of subgraph sets we have to consider.

First, we define a {\em fact} in our semantic graph as the subgraph formed by performing a graph-traversal on a root of the graph (that is, a node with no parents). An example is shown in figure \ref{fig:amr_example_3_merged_s1_highlighted}. By design, the roots of an AMR graph will be verb instances. Therefore, we can intuitively think of the rooted graph traversal as a verb + the required graph pieces to fulfill the verb's arguments. A fact, then, is the the smallest piece of a graph that could be used to fully specify the semantics of a sentence during generation. Let $F$ refer to the set of facts in our graph.

\begin{figure}
\includegraphics[width=\linewidth]{amr_example_3_merged_s1_highlighted.pdf}
\caption{AMR Graph with fact rooted by `s1' highlighted. Two other facts are present, rooted by `d' and `s'.}
\label{fig:amr_example_3_merged_s1_highlighted}
\end{figure}

Given $F$, our set of facts, and the assumption that we do not want to say the exact same thing twice, we can reduce our search-space to the set of partitions of $F$ from size 1 to $|F|$ (a single group with $|F|$ facts to $|F|$ groups each with 1 fact). The size of our candidate set is now given by $B_{|F|}$, where $B_i$ is the $i^{\text{th}}$ Bell number.

\subsubsection{Training}
Our problem then is to find the best partition from the $B_{|F|}$ candidates. To do this, we trained a scoring function using a logistic regression model with class-weighted instances. We assumed that the partitioning given by the sentences in a paragraph was the correct partitioning, and gave it a label of $1$. This means that we had only positive examples in the training set, so we added negative examples by sampling $k$ other partitions from the set of partitions, giving each a label of $0$.

Table \ref{tab:subgraph_selection_features} lists the features extracted for each candidate partition. To determine subgraph similarity, we used
Jaccard similarity, defined to be:
$$J(A,B) = \frac{\lvert A \cap B \rvert}{\lvert A \cup B \rvert}$$

\begin{table}[H]
\centering
\caption{Features used by subgraph partition scorer}
\label{tab:subgraph_selection_features}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Feature}                           & \textbf{Description}                            \\ \midrule
partition\_length                          & Number of groups in the partition               \\
partition\_length\_squared                 & Number of groups in the partition squared       \\
mean/min/max/std\_dev partition\_facts     & Number of facts per partition                   \\
mean/min/max/std\_dev subgraph\_similarity & Pairwise subgraph similarity between all groups \\
mean/min/max/std\_dev verb\_similarity     & Pairwise verb similarity between all groups     \\ \bottomrule
\end{tabular}
\end{table}

@@

Additionally, we used a simulated annealing approach, but only for the
subgraph ordering problem.
